Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can. This subset is based on adapted clone definitions, that are optimized towards automated refactoring. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

None of the surveyed tools had all desired characteristics. Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.

anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}, which goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones. In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.

>>>>

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can. %This subset is based on adapted clone definitions, that are optimized towards automated refactoring. 
Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.

Therefore, we created a tool, CR\footnote{anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}, which goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones. In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
